---
title: "R Code for Replication: Total Population from Population Census"
author: <span style="font-style:normal">Keisuke Kondo (RIETI & RIEB, Kobe University)</span>
date: <span style="font-style:normal">`r format(Sys.time(), '%Y/%m/%d')`</span>
output: html_document
---

# Content

R codes and data for replication (Kondo, 2023)

- Packages
- Municipal Data
- Municipality Converter
- Aggregate Municipal Data of Population Census by Municipality as of 2015
- Verification of Accuracy of Municipality Converter

## Packages

Load the following packages. Install them by `install.packages()` if not installed.

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(purrr)
library(readr)
library(stringr)
library(haven)
```

## Municipal Data 

Load the wide panel data from Japan's Future Committee. Reshape wide panel data to long panel data.

```{r}
#Load Municipal Panel Data from Japan's Future Committee. 
dfCaoPop_wide <- read_dta("data_pop/DTA_cao_pop.dta") %>%
  dplyr::select(-c(pop1970, pop1975))
#From Wide to Long
dfCaoPop_long <- tidyr::gather(dfCaoPop_wide, key = "time", value = "pop", 3:9)
#Add Variable of Year
dfCaoPop_long <- dfCaoPop_long %>%
  dplyr::mutate(year = stringr::str_replace(dfCaoPop_long$time, pattern = "pop", replacement = "")) %>%
  dplyr::select(-time)
dfCaoPop_long$year <- as.numeric(dfCaoPop_long$year)
```

## Municipality Converter

```{r}
#Load Municipality Converter
dfMuniConverter <- readr::read_csv("municipality_converter_en.csv")
```

## Aggregate Municipal Data of Population Census by Municipality as of 2015

```{r}
myFunc <- function(x){
  #Load Data
  dfOld <- read_dta(paste0("data_pop/DTA_estat_pop", x, ".dta"))
  #Add Panel ID and Municipal Names from Municipality Converter
  #Aggregate Municipal Data by Municipality as of 2015
  dfNew <- dplyr::left_join(dfOld, dfMuniConverter, by=c("id_muni" = "merge_id_muni")) %>%
    dplyr::select(id_muni, id_muni2015, name_muni2015, pop) %>%
    dplyr::group_by(id_muni2015) %>%
    dplyr::filter(!is.na(id_muni2015)) %>%
    dplyr::mutate(totalpop = sum(pop)) %>%
    dplyr::mutate(year=x) %>%
    dplyr::select(year, id_muni2015, name_muni2015, totalpop) %>%
    dplyr::distinct()
}
dfPop_long <- purrr::map_dfr(seq(1980, 2010, 5),myFunc)
```

Reshape from long to wide panel data.

```{r}
#Wide Panel Data
dfPop_wide <- tidyr::spread(dfPop_long, key = year, value = totalpop)
#Rename Variable Names
oldvarname <- names(dfPop_wide)[3:length(dfPop_wide)]
newvarname <- paste0("totalpop", oldvarname)
namelist <- setNames(oldvarname, newvarname)
dfPop_wide <- dplyr::rename(dfPop_wide, !!!namelist)
```

## Verification of Accuracy of Municipality Converter

Compare total population between aggregated data and answer data.

```{r}
dfPopJoin <- dplyr::left_join(dfPop_long, dfCaoPop_long, by=c("id_muni2015" = "id_muni", "year" = "year")) %>%
  dplyr::mutate(diff = totalpop - pop)
```

Show differences in total population.

```{r}
dplyr::filter(dfPopJoin, diff!=0)
```
